\subsection{RQ2 : Changes in topics of Stack Overflow questions}
\label{RQ2}

We wanted to observe the changes over time in topics of the questions asked by developers over the time. Hence, we have collected all the posts of the new languages and accumulated them in 6 monthly interval. Then by using the LDA method we have collected topics for each interval for each language.\\
We have noticed a clear division in topics of the questions. From this point of view, we have categorized the age  of language into two parts.

\begin{enumerate}[label=(\Alph*)]

\item \textbf{Evolving state:} In earlier years developers mainly ask about installation or compilation problem and various features, services, SDK documentation, basic programming related topic like regular expression, wild-card, operator overloading, inheritance, session, pointer, concurrency, library support similar to other languages and integration problem in projects like a database connection.

\item \textbf{Matured state:} After some releases, topics become little advanced such as query about frameworks written in that language, thread safety, new feature, network programming, graphics programming, object-relational mapper, deployment systems like docker and cross-platform development.

It is not possible to pinpoint the edge of this states from topics, but the boundary for the \emph{evolving state} or the \emph{matured state} of Swift language is vague to us. Many advances topic like thread safety and cross platform development  appears in the \emph{evolving state} of Swift. The reason is that Swift language inherits many library support, expert users and projects from Objective-C. Either Swift language has no evolving state, or it is too short to be captured in topics of the questions asked by developers.



\end{enumerate}